Dataset of operator-client dialogues aligned with knowledge-base queries

### 2016-06-24 paper.tex
Update on Overleaf.

%Multiple insitutes
%Currently disabled
%
% \iffalse % FIXME enable for blind review and ucomment Single institute with filled values 
\iftrue % FIXME enable for blind review and ucomment Single institute with filled values 
%Multiple institutes are typeset as follows:
\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

\institute{
Insitute 1\\
\email{...}\and
Insitute 2\\
\email{...}
}
\fi

@@

The paper is structured as follows:
XY

@@

\subsubsection{Domain database}
\label{sec:db}

@@

\subsubsection{Client interface}
\label{sec:client}

@@

\subsubsection{Operator database}
\label{sec:operator}
The operator is asked to politely reply the clients needs according the information stored in the database.
In order to provide the information to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
Her or she filters the restaurants using a full text search on the database.
The content of the database is intentional hidden if no filter is specified so the filter has to be used.
The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.

@@

\subsubsection{Asynchronous collection without real-time responses}
\label{sec:async}
We design the crowd-sourcing jobs so the CF contributors are able to work independently to each other.
One conversation is collected through out several rounds of jobs.
The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
As a consequence, multiple contributors participate in submitting responses for single conversation for both roles.

Each utterance in conversation is submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
Note also that the conversation are typically rather short.
The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.

@@

@@

The workers are paid for every submitted response the same amount independently if they play client or operator role.
The roles are assigned randomly.

@@

\subsubsection*{Acknowledgments}
We would like to thank Ond\v{r}ej Du\v{s}ek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.

>>>>

%Multiple insitutes
%Currently disabled
%
% \iffalse % FIXME enable for blind review and ucomment Single institute with filled values

\iftrue % FIXME enable for blind review and ucomment Single institute with filled values 
\author{Firstname Lastname \and Firstname Lastname }
\institute{
Insitute\\
\email{anonym@anonymous}
}
\fi

@@

The paper is structured as follows: The~Section~\ref{sec:repre} motivates the annotations and format of our dataset.
In the Section~\ref{sec:collection} we introduce our collection process using crowd-sourcing.
Section~\ref{sec:props} presents the dataset properties and we list the related work in the~Section~\ref{sec:related}.
We conclude the paper and suggest future work in~Section~\ref{sec:conc}.

@@

\subsection{Domain database}
\label{sec:db}

@@

\subsection{Client interface}
\label{sec:client}

@@

\subsection{Operator interface}
\label{sec:operator}
The operator is asked to politely reply the clients needs according the information stored in the database.
In order to provide the information to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
Her or she filters the restaurants using a full text search on the database.
The content of the database is intentional hidden if no filter is specified so the filter has to be used.
The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.

@@

\subsection{Asynchronous collection without real-time responses}
\label{sec:async}
We design the crowd-sourcing jobs so the CF contributors are able to work independently to each other.
The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
As a consequence, multiple contributors participate in submitting responses for single conversation for both roles.

Each utterance in conversation is submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.

@@

In single job submission we let the workers append to each dialogue a~single response.
Typically, we submit from twenty to thirty partial dialogues with different history lengths.
Some conversations might be just initialized with the auto-generated greetings but most of them store multiple turns collected by CF contributors in the~previous submission.
Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
The workers are paid for every submitted response the same amount independently if they play client or operator role and they typically contribute to multiple conversation during one job submission.
The contributors are assigned roles randomly.

@@

@@

\subsubsection*{Acknowledgments}
We would like to thank Ond\v{r}ej Du\v{s}ek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.
